---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
zzz=read.table("C:\\Users\\Jehyun Cheon\\Desktop\\test\\NAME\\data\\sample.txt",header=TRUE)
knitr::kable(head(zzz, 10))
plot(zzz)

x1=seq(-3,3,length=50)
x2=seq(-4,4,length=60)
f=function(x1,x2){x1^2+x2^2+x1*x2}
y=outer(x1,x2,FUN=f)
persp(x1,x2,y)
contour(x1,x2,y)

library(mapdata)
map('world',fill=TRUE,col=3)
m=map('world',region=c('South Korea','North Korea'))
x=seq(-5,5,length=200)

y=dnorm(x,mean=0,sd=1)
plot(x,y,type="l",lwd=2,col="red")
x=seq(-1,5,length=100)
y=dnorm(x,mean=0,sd=1)
polygon(c(-1,x,5),c(0,y,0),col="lightgray")

data(InsectSprays)
attach(InsectSprays)
knitr::kable(head(InsectSprays, 10))

pie(table(spray))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
